# Matthew Bierman
# CS 4301.002
# March Madness Project

## This script creates each fullTeamData files, which contains all aggregated data for each team from every season (2010-2018)
###### In order to create each fullTeamData file (fullTeamData2010.csv, fullTeamData2011.csv, ..., fullTeamData2018.csv), run the file and set the desired year by changing the value of `currentYear`. For example, `currentYear <- 2018` will create fullTeamData2018.csv. This could have been implemented in a loop that creates every fullTeamData file at once, but you wouldn't be able to see any of the important outputs like `head(fullTeamData)` and `str(fullTeamData)`.

### Set the year for what data to use
##### (2010-2017 for testing, 2018 for Kaggle submission)
```{r}
currentYear <- 2016
```

### Import libraries
```{r}
options(warn=-1)
library(caret)
library(SparkR)
library(dplyr)
library(magrittr)
library(tidyr)
```

### Load Apache Spark
```{r}
sparkR.session()
sc <- sparkR.init(master = "local")
```

### Import datasets
```{r}
# Import regular season data
RegularSeasonDetailedResults <- read.df(path = "Data/RegularSeasonDetailedResults.csv", source = "csv", header = "true")
RegularSeasonDetailedResults <- as.data.frame(RegularSeasonDetailedResults)
RegularSeasonDetailedResults[, c(1:6, 8:34)] <- sapply(RegularSeasonDetailedResults[, c(1:6, 8:34)], as.numeric)
head(RegularSeasonDetailedResults)

# Import submission file
test <- read.df(path = "Data/SampleSubmissionStage2.csv", source = "csv", header = "true")
test <- as.data.frame(test)
test[, c(2)] <- sapply(test[, c(2)], as.numeric)
head(test)

# Import team data
Teams <- read.df(path = "Data/Teams.csv", source = "csv", header = "true")
Teams <- as.data.frame(Teams)
Teams[, c(1, 3:4)] <- sapply(Teams[, c(1, 3:4)], as.numeric)
head(Teams)

# Import coaches data
Coaches <- read.df(path = "Data/TeamCoaches.csv", source = "csv", header = "true")
Coaches <- as.data.frame(Coaches)
Coaches[, c(1:4)] <- sapply(Coaches[, c(1:4)], as.numeric)
head(Coaches)

# Import conferences data
Conferences <- read.df(path = "Data/TeamConferences.csv", source = "csv", header = "true")
Conferences <- as.data.frame(Conferences)
Conferences[, c(1:2)] <- sapply(Conferences[, c(1:2)], as.numeric)
head(Conferences)

# Import conferences (full names) data
ConferencesFullNames <- read.df(path = "Data/Conferences.csv", source = "csv", header = "true")
ConferencesFullNames <- as.data.frame(ConferencesFullNames)
head(ConferencesFullNames)

# Import seed data
Seeds <- read.df(path = "Data/NCAATourneySeeds.csv", source = "csv", header = "true")
Seeds <- as.data.frame(Seeds)
Seeds[, c(1, 3)] <- sapply(Seeds[, c(1, 3)], as.numeric)
head(Seeds)
```

### Prepare datasets for merging with fullTeamData dataset
##### fullTeamData has all data for each team for that year
```{r}
# Remove DayNum column from RegularSeasonDetailedResults dataset
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(2)]

# Convert Seed column in Seeds dataset into an integer (and without conference prefix)
Seeds$Seed <- as.integer(substr(Seeds$Seed, 2, 3))
Seeds <- Seeds[Seeds$Season == currentYear, ]
head(Seeds)

# In training, we have to assume we don't know if the coach will continue to coach for the same team in future years, so remove all rows with a Season that's not the current year or earlier
Coaches <- Coaches[Coaches$Season <= currentYear, ]

# Remove rows where the coach was replaced before the end of the season
Coaches <- Coaches[Coaches$LastDayNum == 77 | Coaches$LastDayNum == 154, ]

# Create countTotalYears dataset with TotalYears column
countTotalYears <- Coaches
countTotalYears$TotalYears <- 1
countTotalYears <- countTotalYears[order(countTotalYears$TeamID), c(5, 6)]
countTotalYears <- as.data.frame(countTotalYears %>% group_by(CoachName) %>% summarise(sum(TotalYears)))
head(countTotalYears)

# Create countUnivYears dataset with TotalYears column
countUnivYears <- Coaches[order(Coaches$TeamID), c(2, 5)]
countUnivYears$TotalYears <- 1
countUnivYears <- as.data.frame(countUnivYears %>% group_by(TeamID, CoachName) %>% summarise(sum(TotalYears)))
head(countUnivYears)

# Create NumWins dataset with Wins and WinsOT columns
RegularSeasonDetailedResults$numWins <- 1
NumWins <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear, c(2, 7, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumWins$NumOT <- ifelse(NumWins$NumOT > 0, 1, 0)
NumWins <- as.data.frame(NumWins %>% group_by(WTeamID) %>% summarise(sum(NumOT), sum(numWins)))
NumWins <- NumWins[, c(1, 3, 2)] %>% set_colnames(c("TeamID", "Wins", "WinsOT"))
head(NumWins)

# Create NumLosses dataset with Losses and LossesOT columns
RegularSeasonDetailedResults$numLosses <- 1
NumLosses <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear, c(4, 7, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumLosses$NumOT <- ifelse(NumLosses$NumOT > 0, 1, 0)
NumLosses <- as.data.frame(NumLosses %>% group_by(LTeamID) %>% summarise(sum(NumOT), sum(numLosses)))
NumLosses <- NumLosses[, c(1, 3, 2)] %>% set_colnames(c("TeamID", "Losses", "LossesOT"))
head(NumLosses)

# Create NumHomeWins dataset with HomeWins column
RegularSeasonDetailedResults$numHomeWins <- 1
NumHomeWins <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear & RegularSeasonDetailedResults$WLoc == "H", c(2, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumHomeWins <- as.data.frame(NumHomeWins %>% group_by(WTeamID) %>% summarise(sum(numHomeWins)))
NumHomeWins <- NumHomeWins %>% set_colnames(c("TeamID", "HomeWins"))
head(NumHomeWins)

# Create NumHomeLosses dataset with HomeLosses column
RegularSeasonDetailedResults$numHomeLosses <- 1
NumHomeLosses <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear & RegularSeasonDetailedResults$WLoc == "H", c(4, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumHomeLosses <- as.data.frame(NumHomeLosses %>% group_by(LTeamID) %>% summarise(sum(numHomeLosses)))
NumHomeLosses <- NumHomeLosses %>% set_colnames(c("TeamID", "HomeLosses"))
head(NumHomeLosses)

# Create NumAwayWins dataset with AwayWins column
RegularSeasonDetailedResults$numAwayWins <- 1
NumAwayWins <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear & RegularSeasonDetailedResults$WLoc == "A", c(2, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumAwayWins <- as.data.frame(NumAwayWins %>% group_by(WTeamID) %>% summarise(sum(numAwayWins)))
NumAwayWins <- NumAwayWins %>% set_colnames(c("TeamID", "AwayWins"))
head(NumAwayWins)

# Create NumAwayLosses dataset with AwayLosses column
RegularSeasonDetailedResults$numAwayLosses <- 1
NumAwayLosses <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear & RegularSeasonDetailedResults$WLoc == "A", c(4, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumAwayLosses <- as.data.frame(NumAwayLosses %>% group_by(LTeamID) %>% summarise(sum(numAwayLosses)))
NumAwayLosses <- NumAwayLosses %>% set_colnames(c("TeamID", "AwayLosses"))
head(NumAwayLosses)

# Create NumNeutralWins dataset with NeutralWins column
RegularSeasonDetailedResults$numNeutralWins <- 1
NumNeutralWins <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear & RegularSeasonDetailedResults$WLoc == "N", c(2, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumNeutralWins <- as.data.frame(NumNeutralWins %>% group_by(WTeamID) %>% summarise(sum(numNeutralWins)))
NumNeutralWins <- NumNeutralWins %>% set_colnames(c("TeamID", "NeutralWins"))
head(NumNeutralWins)

# Create NumNeutralLosses dataset with NeutralLosses column
RegularSeasonDetailedResults$numNeutralLosses <- 1
NumNeutralLosses <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear & RegularSeasonDetailedResults$WLoc == "N", c(4, 34)]
RegularSeasonDetailedResults <- RegularSeasonDetailedResults[, -c(34)]
NumNeutralLosses <- as.data.frame(NumNeutralLosses %>% group_by(LTeamID) %>% summarise(sum(numNeutralLosses)))
NumNeutralLosses <- NumNeutralLosses %>% set_colnames(c("TeamID", "NeutralLosses"))
head(NumNeutralLosses)

# Rearrange RegularSeasonDetailedResults dataset so that it only shows one team per row instead of two teams
RegularSeasonDetailedResults_OneTeam_1 <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear, c(1:3, 8:20)]
RegularSeasonDetailedResults_OneTeam_1 <- RegularSeasonDetailedResults_OneTeam_1 %>% set_colnames(c("Season", "TeamID", "Score", "FGM", "FGA", "FGM3", "FGA3", "FTM", "FTA", "OR", "DR", "Ast", "TO", "Stl", "Blk", "PF"))
RegularSeasonDetailedResults_OneTeam_2 <- RegularSeasonDetailedResults[RegularSeasonDetailedResults$Season == currentYear, c(1, 4:5, 21:33)]
RegularSeasonDetailedResults_OneTeam_2 <- RegularSeasonDetailedResults_OneTeam_2 %>% set_colnames(c("Season", "TeamID", "Score", "FGM", "FGA", "FGM3", "FGA3", "FTM", "FTA", "OR", "DR", "Ast", "TO", "Stl", "Blk", "PF"))
RegularSeasonDetailedResults_OneTeam <- rbind(RegularSeasonDetailedResults_OneTeam_1, RegularSeasonDetailedResults_OneTeam_2)

# Create RegularSeasonDetailedResults_OneTeam dataset with data from RegularSeasonDetailedResults dataset plus FGM2 and FGA2 columns
# FGM2 = 2-pt field goals made
# FGA2 = 2-pt field goals attempted
RegularSeasonDetailedResults_OneTeam$FGM2 <- RegularSeasonDetailedResults_OneTeam$FGM - RegularSeasonDetailedResults_OneTeam$FGM3
RegularSeasonDetailedResults_OneTeam$FGA2 <- RegularSeasonDetailedResults_OneTeam$FGA - RegularSeasonDetailedResults_OneTeam$FGA3
RegularSeasonDetailedResults_OneTeam <- RegularSeasonDetailedResults_OneTeam[, c(2:5, 17:18, 6:16)]
head(RegularSeasonDetailedResults_OneTeam)

# Create Avgs dataset with AvgScore, AvgFGM, AvgFGA, AvgFGM2, AvgFGA2, AvgFGM3, AvgFGA3, AvgFTM, AvgFTA, AvgOR, AvgDR, AvgAst, AvgTO, AvgStl, AvgBlk, AvgPF
Avgs <- as.data.frame(RegularSeasonDetailedResults_OneTeam %>% group_by(TeamID) %>% summarise(mean(Score), mean(FGM), mean(FGA), mean(FGM2), mean(FGA2), mean(FGM3), mean(FGA3), mean(FTM), mean(FTA), mean(OR), mean(DR), mean(Ast), mean(TO), mean(Stl), mean(Blk), mean(PF)))
Avgs <- Avgs %>% set_colnames(c("TeamID", "AvgScore", "AvgFGM", "AvgFGA", "AvgFGM2", "AvgFGA2", "AvgFGM3", "AvgFGA3", "AvgFTM", "AvgFTA", "AvgOR", "AvgDR", "AvgAst", "AvgTO", "AvgStl", "AvgBlk", "AvgPF"))
head(Avgs)
```

### Create fullTeamData dataset for all team information
* TeamID = unique ID number of team
* TeamName = name of team
* ConfAbbrev = name of conference team is in (abbreviation)
* ConfFullName = name of conference team is in (full name)
* CoachName = name of coach
* TotalCoachYears = number of years the coach has been a coach for any team
* TotalCurrYears = number of years the coach has been a coach for his current team
* Seed = ranking of the team (1 through 16, 20 if unranked)
* Wins = number of wins in regular season (Number of wins = number of OT wins + number of non-OT wins)
* WinsOT = number of wins in overtime in regular season
* Losses = number of losses in regular season (Number of losses = number of OT losses + number of non-OT losses)
* LossesOT = number of losses in overtime in regular season
* HomeWins = number of wins at home in regular season
* HomeLosses = number of losses at home in regular season
* AwayWins = number of wins at away in regular season
* AwayLosses = number of losses at away in regular season
* NeutralWins = number of wins at neutral in regular season
* NeutralLosses = number of losses at neutral in regular season
* NeutralWinsPct = percentage of neutral wins = neutral wins / overall wins
* NeutralLossesPct = percentage of neutral losses = neutral losses / overall losses
* AvgScore = average points scored
* AvgFGM = average field goals made
* AvgFGA = average field goals attempted
* AvgFGM2 = average 2-pt field goals made (AvgFGM2 = AvgFGM - AvgFGM3)
* AvgFGA2 = average 2-pt field goals attempted (AvgFGA2 = AvgFGA - AvgFGA3)
* AvgFGM3 = average 3-pt field goals made
* AvgFGA3 = average 3-pt field goals attempted
* AvgFTM = average free throws made
* AvgFTA = average free throws attempted
* AvgOR = average offensive rebounds
* AvgDR = average defensive rebounds
* AvgAst = average assists
* AvgTO = average turnovers
* AvgStl = average steals
* AvgBlk = average blocks
* AvgPF = average personal fouls committed

```{r}
fullTeamData <- test
head(fullTeamData)

# Create dataframe with all possible teams (ID and TeamName)
fullTeamData <- Teams[, c(1, 2)]

# Add coaches to fullTeamData
fullTeamData <- merge(fullTeamData, Coaches, by = c("TeamID"), sort = F)
fullTeamData <- fullTeamData[fullTeamData$Season == currentYear, -c(3:5)]

# Add conferences to fullTeamData
fullTeamData <- merge(fullTeamData, Conferences, by = c("TeamID"), sort = F)
fullTeamData <- fullTeamData[fullTeamData$Season == currentYear, -c(4)]

# Add conferences (full names) to fullTeamData
fullTeamData <- merge(fullTeamData, ConferencesFullNames, by = c("ConfAbbrev"))
fullTeamData <- fullTeamData[order(fullTeamData$TeamID), c(2, 3, 4, 1, 5)]

# Add Seed to fullTeamData
fullTeamData <- merge(fullTeamData, Seeds, by = c("TeamID"), all = TRUE)
fullTeamData <- fullTeamData[, -c(6)]

# Add countTotalYears to fullTeamData
fullTeamData <- merge(fullTeamData, countTotalYears, by = c("CoachName"))

# Add CurrCoachYears to fullTeamData
fullTeamData <- merge(fullTeamData, countUnivYears, by = c("CoachName", "TeamID"))

# Add Wins and WinsOT to fullTeamData
fullTeamData <- merge(fullTeamData, NumWins, by = c("TeamID"), all = TRUE)

# Add Losses and LossesOT to fullTeamData
fullTeamData <- merge(fullTeamData, NumLosses, by = c("TeamID"), all = TRUE)

# Add HomeWins to fullTeamData
fullTeamData <- merge(fullTeamData, NumHomeWins, by = c("TeamID"), all = TRUE)

# Add HomeLosses to fullTeamData
fullTeamData <- merge(fullTeamData, NumHomeLosses, by = c("TeamID"), all = TRUE)

# Add AwayWins to fullTeamData
fullTeamData <- merge(fullTeamData, NumAwayWins, by = c("TeamID"), all = TRUE)

# Add AwayLosses to fullTeamData
fullTeamData <- merge(fullTeamData, NumAwayLosses, by = c("TeamID"), all = TRUE)

# Add NeutralWins to fullTeamData
fullTeamData <- merge(fullTeamData, NumNeutralWins, by = c("TeamID"), all = TRUE)

# Add NeutralLosses to fullTeamData
fullTeamData <- merge(fullTeamData, NumNeutralLosses, by = c("TeamID"), all = TRUE)

# Add NeutralWinsPct and NeutralLossesPct to fullTeamData
fullTeamData$NeutralWinsPct <- fullTeamData$NeutralWins / fullTeamData$Wins
fullTeamData$NeutralLossesPct <-  fullTeamData$NeutralLosses / fullTeamData$Losses

# Add AvgScore, AvgFGM, AvgFGA, AvgFGM2, AvgFGA2, AvgFGM3, AvgFGA3, AvgFTM, AvgFTA, AvgOR, AvgDR, AvgAst, AvgTO, AvgStl, AvgBlk, and AvgPF to fullTeamData
fullTeamData <- merge(fullTeamData, Avgs, by = c("TeamID"))

# This shows the number of NA's per column
# 287 NA's in Seed
# 1 NA in HomeWins
# 8 NA's in AwayWins
# 5 NA's in AwayLosses
# 103 NA's in NeutralWins
# 103 NA's in NeutralWinsPct
# 48 NA's in NeutralLosses
# 48 NA's in NeutralLossesPct
summary(fullTeamData)

# Replace all NA's with 0 for all columns
fullTeamData[is.na(fullTeamData)] <- 0

# Replace all 0's with 20 in the Seed column, since 0 means unseeded and an unseeded team is not better than a #1 seed team
fullTeamData[fullTeamData$Seed == 0, c("Seed")] <- 20

# Fix column names and reorder columns
fullTeamData <- fullTeamData[order(fullTeamData$TeamID), c(1, 3:5, 2, 7:8, 6, 9:36)]
fullTeamData <- fullTeamData %>% set_colnames(c("TeamID", "TeamName", "ConfAbbrev", "ConfFullName", "CoachName", "TotalCoachYears", "CurrCoachYears", "Seed", "Wins", "WinsOT", "Losses", "LossesOT", "HomeWins", "HomeLosses", "AwayWins", "AwayLosses", "NeutralWins", "NeutralLosses", "NeutralWinsPct", "NeutralLossesPct", "AvgScore", "AvgFGM", "AvgFGA", "AvgFGM2", "AvgFGA2", "AvgFGM3", "AvgFGA3", "AvgFTM", "AvgFTA", "AvgOR", "AvgDR", "AvgAst", "AvgTO", "AvgStl", "AvgBlk", "AvgPF"))

# Display all data
str(fullTeamData)
```

### Export fullTeamData dataset to fullTeamData[Year].csv
```{r}
fileName <- paste("Data/fullTeamData", currentYear, ".csv", sep = "")
write.csv(fullTeamData, file = fileName, row.names = FALSE)
```