# Matthew Bierman
# CS 4301.002
# March Madness Project

## This script creates the submission file for the Kaggle competition
###### All of the outputs for creating the train and test datasets can be seen in this script that could not be seen in the Testing script

### Import libraries
```{r}
options(warn=-1)
library(caret)
library(SparkR)
library(dplyr)
library(magrittr)
library(tidyr)
```

### Load Apache Spark
```{r}
sparkR.session()
sc <- sparkR.init(master = "local")
```

### Import datasets
```{r}
# Import full team data for 2018
fullTeamData <- read.df(path = "Data/fullTeamData2018.csv", source = "csv", header = "true")
fullTeamData <- as.data.frame(fullTeamData)
fullTeamData[, c(1, 36)] <- sapply(fullTeamData[, c(1, 36)], as.numeric)

# Import submission file
test <- read.df(path = "Data/SampleSubmissionStage2.csv", source = "csv", header = "true")
test <- as.data.frame(test)
test[, c(2)] <- sapply(test[, c(2)], as.numeric)
```

### Set the year for what data to use
##### (2018 for Kaggle submission)
```{r}
currentYear <- 2018
```

### Create train dataset
##### Train = regular season
```{r}
# Submission file has ID in the form of Year_Team1ID_Team2ID, Result is 1 if Team1 wins, 0 if Team2 wins
# Create ID for each game, where train_1 has all Team1's winning and train_2 has all Team2's winning
train <- read.df(path = "Data/RegularSeasonCompactResults.csv", source = "csv", header = "true")
train <- as.data.frame(train)
train[, c(1:6, 8)] <- sapply(train[, c(1:6, 8)], as.numeric)
train_1 <- train[, c(1, 3, 5)]
train_1$ID <- paste(train_1$Season, train_1$WTeamID, train_1$LTeamID, sep = "_")
train_1$Result <- 1
train_2 <- train[, c(1, 3, 5)]
train_2$ID <- paste(train_2$Season, train_2$LTeamID, train_2$WTeamID, sep = "_")
train_2$Result <- 0

# Combine train_1 and train_2 into train, which has every game played from that season with both Team ID's and the result
train <- rbind(train_1, train_2)
train <- train[train$Season == currentYear, ]
train <- train[order(train$ID), ]
train$WTeamID <- as.integer(substr(train$ID, 6, 9))
train$LTeamID <- as.integer(substr(train$ID, 11, 14))
train <- train %>% set_colnames(c("Season", "TeamID.x", "TeamID.y", "ID", "Result"))
head(train)

# Add team data from fullTeamData to each team in train dataset
fullTeamData_2 <- fullTeamData
colnames(fullTeamData_2)[1] <- "TeamID.x"
train <- merge(train, fullTeamData_2, by = c("TeamID.x"))
colnames(fullTeamData_2)[1] <- "TeamID.y"
train <- merge(train, fullTeamData_2, by = c("TeamID.y"))
train <- train[order(train$ID), ]
train[, c(10:40, 45:75)] <- sapply(train[, c(10:40, 45:75)], as.numeric)

dim(train)
head(train)
```

### Create test dataset
##### Test = March Madness postseason tournament
```{r}
# Get both Team ID's from ID
test <- read.df(path = "Data/SampleSubmissionStage2.csv", source = "csv", header = "true")
test <- as.data.frame(test)
test[, c(2)] <- sapply(test[, c(2)], as.numeric)
test$Season <- as.integer(substr(test$ID, 1, 4))
test$TeamID.x <- as.integer(substr(test$ID, 6, 9))
test$TeamID.y <- as.integer(substr(test$ID, 11, 14))
test <- test[, c(3:5, 1, 2)]

dim(test)
head(test)

# Merge fullTeamData with test set
fullTeamData_2 <- fullTeamData
colnames(fullTeamData_2)[1] <- "TeamID.x"
test <- merge(test, fullTeamData_2, by = c("TeamID.x"))
colnames(fullTeamData_2)[1] <- "TeamID.y"
test <- merge(test, fullTeamData_2, by = c("TeamID.y"))
test <- test[order(test$ID), ]
test[, c(10:40, 45:75)] <- sapply(test[, c(10:40, 45:75)], as.numeric)
str(test)
```

### Create Diff columns for each feature for both train and test datasets
* SeedDiff = Team 1 Seed - Team 2 Seed
* TotalCoachYearsDiff = Team 1 TotalCoachYears - Team 2 TotalCoachYears
* CurrCoachYearsDiff = Team 1 CurrCoachYears - Team 2 CurrCoachYears
* WinsDiff = Team 1 Wins - Team 2 Wins
* LossesDiff = Team 1 Losses - Team 2 Losses
* NeutralWinsDiff = Team 1 NeutralWins - Team 2 NeutralWins
* NeutralLossesDiff = Team 1 NeutralLosses - Team 2 NeutralLosses
* NeutralWinsPctDiff = Team 1 NeutralWinsPct - Team 2 NeutralWinsPct
* NeutralLossesPctDiff = Team 1 NeutralLossesPct - Team 2 NeutralLossesPct
* AvgScoreDiff = Team 1 AvgScore - Team 2 AvgScore
* AvgFGMDiff = Team 1 AvgFGM - Team 2 AvgFGM
* AvgFGADiff = Team 1 AvgFGA - Team 2 AvgFGA
* AvgFGM2Diff = Team 1 AvgFGM2 - Team 2 AvgFGM2
* AvgFGA2Diff = Team 1 AvgFGA2 - Team 2 AvgFGA2
* AvgFGM3Diff = Team 1 AvgFGM3 - Team 2 AvgFGM3
* AvgFGA3Diff = Team 1 AvgFGA3 - Team 2 AvgFGA3
* AvgFTMDiff = Team 1 AvgFTM - Team 2 AvgFTM
* AvgFTADiff = Team 1 AvgFTA - Team 2 AvgFTA
* AvgORDiff = Team 1 AvgOR - Team 2 AvgOR
* AvgDRDiff = Team 1 AvgDR - Team 2 AvgDR
* AvgAstDiff = Team 1 AvgAst - Team 2 AvgAst
* AvgTODiff = Team 1 AvgTO - Team 2 AvgTO
* AvgStlDiff = Team 1 AvgStl - Team 2 AvgStl
* AvgBlkDiff = Team 1 AvgBlk - Team 2 AvgBlk
* AvgPFDiff = Team 1 AvgPF - Team 2 AvgPF
```{r}
# Add SeedDiff column to both datasets
train$SeedDiff <- train$Seed.x - train$Seed.y
test$SeedDiff <- test$Seed.x - test$Seed.y

# Add TotalCoachYearsDiff column to both datasets
train$TotalCoachYearsDiff <- train$TotalCoachYears.x - train$TotalCoachYears.y
test$TotalCoachYearsDiff <- test$TotalCoachYears.x - test$TotalCoachYears.y

# Add CurrCoachYearsDiff column to both datasets
train$CurrCoachYearsDiff <- train$CurrCoachYears.x - train$CurrCoachYears.y
test$CurrCoachYearsDiff <- test$CurrCoachYears.x - test$CurrCoachYears.y

# Add WinsDiff column to both datasets
train$WinsDiff <- train$Wins.x - train$Wins.y
test$WinsDiff <- test$Wins.x - test$Wins.y

# Add LossesDiff column to both datasets
train$LossesDiff <- train$Losses.x - train$Losses.y
test$LossesDiff <- test$Losses.x - test$Losses.y

# Add NeutralWinsDiff column to both datasets
train$NeutralWinsDiff <- train$NeutralWins.x - train$NeutralWins.y
test$NeutralWinsDiff <- test$NeutralWins.x - test$NeutralWins.y

# Add NeutralLossesDiff column to both datasets
train$NeutralLossesDiff <- train$NeutralLosses.x - train$NeutralLosses.y
test$NeutralLossesDiff <- test$NeutralLosses.x - test$NeutralLosses.y

# Add NeutralWinsPctDiff column to both datasets
train$NeutralWinsPctDiff <- train$NeutralWinsPct.x - train$NeutralWinsPct.y
test$NeutralWinsPctDiff <- test$NeutralWinsPct.x - test$NeutralWinsPct.y

# Add NeutralLossesPctDiff column to both datasets
train$NeutralLossesPctDiff <- train$NeutralLossesPct.x - train$NeutralLossesPct.y
test$NeutralLossesPctDiff <- test$NeutralLossesPct.x - test$NeutralLossesPct.y

# Add AvgScoreDiff column to both datasets
train$AvgScoreDiff <- train$AvgScore.x - train$AvgScore.y
test$AvgScoreDiff <- test$AvgScore.x - test$AvgScore.y

# Add AvgFGMDiff column to both datasets
train$AvgFGMDiff <- train$AvgFGM.x - train$AvgFGM.y
test$AvgFGMDiff <- test$AvgFGM.x - test$AvgFGM.y

# Add AvgFGADiff column to both datasets
train$AvgFGADiff <- train$AvgFGA.x - train$AvgFGA.y
test$AvgFGADiff <- test$AvgFGA.x - test$AvgFGA.y

# Add AvgFGM2Diff column to both datasets
train$AvgFGM2Diff <- train$AvgFGM2.x - train$AvgFGM2.y
test$AvgFGM2Diff <- test$AvgFGM2.x - test$AvgFGM2.y

# Add AvgFGA2Diff column to both datasets
train$AvgFGA2Diff <- train$AvgFGA2.x - train$AvgFGA2.y
test$AvgFGA2Diff <- test$AvgFGA2.x - test$AvgFGA2.y

# Add AvgFGM3Diff column to both datasets
train$AvgFGM3Diff <- train$AvgFGM3.x - train$AvgFGM3.y
test$AvgFGM3Diff <- test$AvgFGM3.x - test$AvgFGM3.y

# Add AvgFGA3Diff column to both datasets
train$AvgFGA3Diff <- train$AvgFGA3.x - train$AvgFGA3.y
test$AvgFGA3Diff <- test$AvgFGA3.x - test$AvgFGA3.y

# Add AvgFTMDiff column to both datasets
train$AvgFTMDiff <- train$AvgFTM.x - train$AvgFTM.y
test$AvgFTMDiff <- test$AvgFTM.x - test$AvgFTM.y

# Add AvgFTADiff column to both datasets
train$AvgFTADiff <- train$AvgFTA.x - train$AvgFTA.y
test$AvgFTADiff <- test$AvgFTA.x - test$AvgFTA.y

# Add AvgORDiff column to both datasets
train$AvgORDiff <- train$AvgOR.x - train$AvgOR.y
test$AvgORDiff <- test$AvgOR.x - test$AvgOR.y

# Add AvgDRDiff column to both datasets
train$AvgDRDiff <- train$AvgDR.x - train$AvgDR.y
test$AvgDRDiff <- test$AvgDR.x - test$AvgDR.y

# Add AvgAstDiff column to both datasets
train$AvgAstDiff <- train$AvgAst.x - train$AvgAst.y
test$AvgAstDiff <- test$AvgAst.x - test$AvgAst.y

# Add AvgTODiff column to both datasets
train$AvgTODiff <- train$AvgTO.x - train$AvgTO.y
test$AvgTODiff <- test$AvgTO.x - test$AvgTO.y

# Add AvgStlDiff column to both datasets
train$AvgStlDiff <- train$AvgStl.x - train$AvgStl.y
test$AvgStlDiff <- test$AvgStl.x - test$AvgStl.y

# Add AvgBlkDiff column to both datasets
train$AvgBlkDiff <- train$AvgBlk.x - train$AvgBlk.y
test$AvgBlkDiff <- test$AvgBlk.x - test$AvgBlk.y

# Add AvgPFDiff column to both datasets
train$AvgPFDiff <- train$AvgPF.x - train$AvgPF.y
test$AvgPFDiff <- test$AvgPF.x - test$AvgPF.y

# Remove .x and .y columns (will be using Diff columns for Logistic Regression)
train <- train[, c(4, 5, 76:100, 6, 41)]
test <- test[, c(4, 5, 76:100, 6, 41)]
str(test)
```

### Perform Logistic Regression v5 -- Using only SeedDiff
```{r}
train_spark <- as.DataFrame(train)
test_spark <- as.DataFrame(test)

# Logistic Regression Model
fit_spark <- spark.logit(train_spark, Result ~ SeedDiff, regParam = 0.3)
summary(fit_spark)

# Predicted values from test set
pred_spark <- predict(fit_spark, test_spark)
pred_spark <- as.data.frame(pred_spark)
pred_spark <- t(apply(pred_spark, 1, FUN = function(df) {
    x <- SparkR:::callJMethod(df$probability, "apply", as.integer(0))
    y <- SparkR:::callJMethod(df$probability, "apply", as.integer(1))
    c(x, y)
}))[, 1]
test$Pred <- pred_spark
test$PredRounded <- ifelse(test$Pred > 0.5, 1, 0)

# Round extreme values to prevent high log loss
test$Pred <- ifelse(test$Pred > 0.999, 0.999, test$Pred)
test$Pred <- ifelse(test$Pred < 0.001, 0.001, test$Pred)
```

### Finalize results, export to .csv
```{r}
# Write winning percentage with team names (makes it easier for creating bracket)
test$forBracket <- paste(round(test$Pred * 100, 2), "% chance that ", test$TeamName.x, " beats ", test$TeamName.y, sep = "")
  
# Export predictions to csv
write.csv(test[, c(1:2)], file = "submission_v1.csv", row.names = FALSE)
write.csv(test[, c(1:2, 31)], file = "submission_v1_forBracket.csv", row.names = FALSE)
```

### Perform Logistic Regression v6 -- Using multiple features with interaction effects
```{r}
train_spark <- as.DataFrame(train)
test_spark <- as.DataFrame(test)

# Logistic Regression Model
fit_spark <- spark.logit(train_spark, Result ~ SeedDiff + NeutralWinsDiff + SeedDiff:WinsDiff:NeutralWinsDiff + SeedDiff:LossesDiff:NeutralWinsDiff + CurrCoachYearsDiff:LossesDiff:NeutralWinsDiff, regParam = 0.3)
summary(fit_spark)

# Predicted values from test set
pred_spark <- predict(fit_spark, test_spark)
pred_spark <- as.data.frame(pred_spark)
pred_spark <- t(apply(pred_spark, 1, FUN = function(df) {
    x <- SparkR:::callJMethod(df$probability, "apply", as.integer(0))
    y <- SparkR:::callJMethod(df$probability, "apply", as.integer(1))
    c(x, y)
}))[, 1]
test$Pred <- pred_spark
test$PredRounded <- ifelse(test$Pred > 0.5, 1, 0)

# Round extreme values to prevent high log loss
test$Pred <- ifelse(test$Pred > 0.999, 0.999, test$Pred)
test$Pred <- ifelse(test$Pred < 0.001, 0.001, test$Pred)
```

### Finalize results, export to .csv
```{r}
# Write winning percentage with team names (makes it easier for creating bracket)
test$forBracket <- paste(round(test$Pred * 100, 2), "% chance that ", test$TeamName.x, " beats ", test$TeamName.y, sep = "")
  
# Export predictions to csv
write.csv(test[, c(1:2)], file = "submission_v2.csv", row.names = FALSE)
write.csv(test[, c(1:2, 31)], file = "submission_v2_forBracket.csv", row.names = FALSE)
```